Instant Continuation Marks--Just Add $\lambda$

### 2012-09-26 paper.tex
Really, the title is the best thing here.

\title{A Correct Compiler for Continuation Marks}

@@

A meaning-preserving transformation should commute with evaluation. By this, we mean that the following property should hold.

@@

This diagram captures the property that a meaning-preserving transformation should commute with evaluation. More succinctly, 
\begin{equation}
\label{meaning-preservation-property}
p\cmrrs v\implies\C{p}\lvrrs\C{v}
\end{equation}

@@

% talk about continuity of chi

@@

\section{Related Work}

[Other people] have made a strong case for continuation marks.

@@

>>>>

\title{Instant Continuation Marks--Just Add $\lambda$}

@@

A meaning-preserving transformation should commute with evaluation. By this, we mean that the following property should hold for programs $p\in\lambda_{cm}$.

@@

This diagram captures the property that a meaning-preserving transformation commutes with evaluation. More succinctly, 
\begin{equation}
\label{meaning-preservation-property}
p\cmrrs v\implies\C{p}\lvrrs\C{v}
\end{equation}

@@

@@

\section{Continuation Marks in JavaScript}

% add stuff to language to express factorial
% define transformation of new constructs
% transform factorial function
% transliterate it to JS
% see continuation marks in JS

% we can add continuation marks to the compiler, but we can't deploy a virtual machine wherever we want. We need to leverage the existing, entrenched virtual machines. One approach would be to

Given that we can express continuation marks in the \lc, we can see that the only thing necessary for continuation marks is first-class functions. JavaScript is a ubiquitous higher-order language that lacks continuation marks. Clements et al. experimentally added continuation marks to JavaScript by directly modifying Mozilla's Rhino implementation \cite{clements2008implementing}. This is a natural fit as the implementation is designed to optimize tail calls providing a venue in which the full semantics of continuation marks can be observed.

Many implementations do not optimize tail calls. We could modify these implementations to first optimize tail calls and then support continuation marks, but this does nothing to the existing, entrenched virtual machines in use today. For this reason, we define a superset of JavaScript with continuation marks and a transformation to base JavaScript. The transformation utilizes the tail-position flag and mark-passing style of the \lc\ transform.

functions receive two additional arguments
if a call is in tail position, pass that flag.
I don't know.

We transliterate

@@

Continuation marks support a bevy of instrumentation tools and advanced language features in a generalized, portable way. Despite their demonstrated utility, they have not yet found their way into most languages. A verified characterization of continuation marks in a pure computational language provides implementors of higher-order languages a correct compiler for continuation marks.

Stack inspection is a common approach for instrumentation and dynamic

Instrumentation tools abound, and stack inspection is a common method to in

Stack inspection is a common approach to natural method to obtain dynamic information, but typical implementation
